Parallel Multi-objective Optimization Method for Finding Complete Set of Weakly Efficient Solutions

### 2017-07-27 2017/URAL-PDC/u_pdc_paper.tex

\usepackage[english]{babel}
\usepackage{amsmath,amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{tabularx}
\DeclareMathOperator{\sign}{sign}
\newcolumntype{K}[1]{>{\centering\arraybackslash}p{#1}}
%
\begin{document}
%
\mainmatter              % start of the contributions
%
\title{Parallel Multi-objective Optimization Using Information Framework for
Constructing Global Optimization Algorithms}
%
\titlerunning{Parallel Multi-objective Optimization}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Vladislav V. Sovrasov}
%
\authorrunning{Vladislav V. Sovrasov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Vladislav V. Sovrasov}
%
\institute{State University of Nizhny Novgorod, Nizhny Novgorod, Russia\\
\email{sovrasov.vlad@gmail.com}}

@@

\section{Description of the Parallel Algorithm With Local Refinement}
\label{sec:algorithm}
Let us consider a scalarization scheme for the reduced problem (\(\ref{eq:problem}\)),
presented in~\cite{markinStrongin1993}. Let
\begin{eqnarray*}
  \varphi(x)=\max\{h(x,y):y\in [0,1]\},x\in [0,1],\\
  h(x,y)=\max\{f_i(x)-f_i(y):1\leqslant i\leqslant\nu\}.
\end{eqnarray*}
Let us consider a scalar problem
\begin{equation}
  \label{eq:aux_problem}
  \varphi^*=\min\{\varphi(x):x\in [0,1]\}.
\end{equation}

@@

>>>>

\usepackage[english]{babel}
\usepackage{amsmath,amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{tabularx}
\DeclareMathOperator{\sign}{sign}
\newcolumntype{K}[1]{>{\centering\arraybackslash}p{#1}}
%
\begin{document}
%
\mainmatter              % start of the contributions
%
\title{Parallel Multi-objective Optimization Method for Finding Complete Set of Weakly Efficient Solutions
%Using Information Framework for Constructing Global Optimization Algorithms
}
%
\titlerunning{Parallel Multi-objective Optimization}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Vladislav V. Sovrasov}
%
\authorrunning{Vladislav V. Sovrasov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Vladislav V. Sovrasov}
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia\\
\email{sovrasov.vlad@gmail.com}}

@@

\section{Description of the Parallel Algorithm With Local Refinement}
\label{sec:algorithm}
Let us consider a scalarization scheme for the reduced problem (\(\ref{eq:problem}\)),
presented in~\cite{markinStrongin1993}. Let
\begin{eqnarray*}
  \varphi(x)=\max\{h(x,y):y\in [0,1]\},x\in [0,1],\\
  h(x,y)=\max\{f_i(x)-f_i(y):1\leqslant i\leqslant m\}.
\end{eqnarray*}
Let us consider a scalar problem
\begin{equation}
  \label{eq:aux_problem}
  \varphi^*=\min\{\varphi(x):x\in [0,1]\}.
\end{equation}

@@

The algorithm for solving problem (\ref{eq:problem}) involves constructing a sequence of points $x^i$, where the values of the objective functions are calculated. Let us call the functions values calculation process (including construction of image $y^i=y(x^i)$) the trial, and the tuple $\{x^i, y^i , f_1(y^i), ... f_m(y^i)\}$, the trial result. At each iteration $p$ trials is carried out in parallel, and the set of tuples 
\[ 
\{x^i, y^i , f_1(y^i), ... f_m(y^i)\}, 1 \leq i \leq k=np,
\] 
makes up the search data collected using the method after carrying out $n$ steps. The rules that define the work of a parallel multi-objective algorithm are as follows.
